DOpElib:\\ Differential Equations and Optimization Environment

### 2018-10-17 Examples/Documentation/tests.tex
add examples to parallel-dev

\begin{remark}
Please keep in mind that there are two optimization examples that 
need external packages to be able to run successfully. These tests will
fail if these libraries are not installed!
\end{remark}

>>>>

\section{Tests with third-party packages}
Please keep in mind that DOpElib does not 
only link to deal.II but also to third party libraries.
If these libraries are not installed, the respective regression tests 
will fail.

Currently the following examples link to third-party examples:
\begin{itemize}
\item \texttt{OPT/StatPDE/Example6}: IPOPT
\item \texttt{OPT/StatPDE/Example8}: SNOPT
\item \texttt{PDE/StatPDE/Example10}: Trilinos (via deal.II)
\end{itemize}

### 2018-10-17 Examples/OPT/StatPDE/Example1/content.tex
add examples to parallel-dev

\subsubsection{\texttt{main.cc}}
Finally, the main file of the optimization examples does not look very much 
different than for pure PDE computations - which is one of the crucial aims 
of our library. 
Here, instead of using a \texttt{pdeproblemcontainer}, we use 
now an \texttt{optproblemcontainer} which can assemble all additionally needed informations,
such as adjoint and tangent PDEs. 
Furthermore, we define \texttt{ReducedNewtonAlgorithm} and 
\texttt{ReducedTrustregion\underline{ }NewtonAlgorithm}
to solve the optimization problem with a linesearch and a trust-region Newton algorithm.
Of course one would be sufficient, but we wanted to show how to change optimization 
solvers easily using \texttt{DOpElib}.

Next, in the body of the main file, we introduce a second FE function for the 
control variable. Then, we define 
a \texttt{COSTFUNCTIONAL}. Finally, the problem is either solved 
by calling \texttt{Alg.Solve(q)} and/or the user might check if the 
derivatives are implemented correctly by calling 
\texttt{Alg.CheckGrads} or \texttt{Alg.CheckHessian}. The latter 
two functionalities are highly recommended to check your
implementation before wondering about your results.

>>>>

\subsubsection{\texttt{main.cc}}
Finally, the main file of the optimization examples does not look very much 
different than for pure PDE computations - which is one of the crucial aims 
of our library. 
Here, instead of using a \texttt{pdeproblemcontainer}, we use 
now an \texttt{optproblemcontainer} which can assemble all additionally needed informations,
such as adjoint and tangent PDEs. 
Furthermore, we define \texttt{ReducedNewtonAlgorithm} and 
\texttt{ReducedTrustregion\underline{ }NewtonAlgorithm}
to solve the optimization problem with a linesearch and a trust-region Newton algorithm.
Of course one would be sufficient, but we wanted to show how to change optimization 
solvers easily using \texttt{DOpElib}.\\
Next, in the body of the main file, we introduce a second FE function for the 
control variable. Then, we define 
a \texttt{COSTFUNCTIONAL}. Finally, the problem is either solved 
by calling \texttt{Alg.Solve(q)} and/or the user might check if the 
derivatives are implemented correctly by calling 
\texttt{Alg.CheckGrads} or \texttt{Alg.CheckHessian}. The latter 
two functionalities are highly recommended to check your
implementation before wondering about your results.\\
Finally, this example uses a DWR-error estimator to estimate the 
error made in the cost functional. In contrast to the 
error estimation for PDEs here, we have to include the error in the
control by using the \texttt{HigherOrderDWRContainerControl}.

### 2018-10-17 Examples/OPT/StatPDE/Example10/content.tex
add examples to parallel-dev

\subsubsection{General problem description}
This example is similar to Example~\ref{OPT_Stat_Param_Nonlin_Fluid}.
The notable difference in the setting is that now, the boundary control areas, 
where the fluid can be sucked out of the domain, are in front of the 
circular inclusion. Hense the drag
\[
k(v,p) = \int_{\Gamma_O} n\cdot \sigma(v,p)\cdot d \, ds,
\]
where $\Gamma_O$ denotes the cylinder boundary, and $d$ is a vector in the
direction of the mean in-flow can become negative, i.e., minimizing the 
value of $k(v,p)$ is no longer viable.

Instead, we consider the objective 
\[
K(q,v,p) = |k(v,p)|^2 + \frac{\alpha}{2}||q - q_0||^2
\] 
is to be minimized.

@@

For higher derivatives, we notice that for a differentiable functions $g,f\colon \mathbb R\rightarrow \mathbb R$
it holds for the directional derivative in direction $\delta u$
\begin{align*}
 \left((g\left(\int f(u(x))\,\mathrm{d}x\right)\right)'\delta u
  &= g'(\int f(u(x))\,\mathrm{d}x) \int f'(u(x)) \delta u(x) \mathrm{d}x \\
  &= \int g'(\int f(u(x))\,\mathrm{d}x) f'(u(x)) \delta u(x) \mathrm{d}x 
\end{align*}
Consequently, the first derivative can be calculated with only a single integration
-- as a boundary integral in the present example.

>>>>

\subsubsection{General problem description}
This example is similar to Example~\ref{OPT_Stat_Param_Nonlin_Fluid}.
The notable difference in the setting is that now, the boundary control areas, 
where the fluid can be sucked out of the domain, are in front of the 
circular inclusion. Hence the drag
\[
k(v,p) = \int_{\Gamma_O} n\cdot \sigma(v,p)\cdot d \, \mathrm{d}s,
\]
where $\Gamma_O$ denotes the cylinder boundary, and $d$ is a vector in the
direction of the mean in-flow can become negative, i.e., minimizing the 
value of $k(v,p)$ is no longer viable.

Instead, we consider the objective 
\[
K(q,v,p) = \frac{1}{2}|k(v,p)|^2 + \frac{\alpha}{2}||q - q_0||^2
\] 
is to be minimized.

@@

For higher derivatives, we notice that for a differentiable functions $g,f\colon \mathbb R\rightarrow \mathbb R$
it holds for the directional derivative in direction $\delta u$
\begin{align*}
 \left((g\left(\int f(u(x))\,\mathrm{d}x\right)\right)'\delta u
  &= g'(\int f(u(x))\,\mathrm{d}x) \int f'(u(x)) \delta u(x) \mathrm{d}x \\
  &= \int g'(\int f(u(x))\,\mathrm{d}x) f'(u(x)) \delta u(x) \mathrm{d}x 
\end{align*}
Consequently, the first derivative can be calculated with only a single integration
-- as a boundary integral in the present example where the 
factor $g'$ can be calculated using the drag value in the 
last iterate  
\[
g'(k(v,p)) \quad\text{and}\quad k'(v,p)\delta u(x) = k(\delta v, \delta p)
\]
since the drag is linear in $(v,p)$.

For the second derivative, we can calculate in the directions $\delta u$ and $\tau u$
by the following observation 
\begin{align*}
 \left(g\left(\int f(u(x))\,\mathrm{d}x\right)\right)''&(\delta u,\tau u)\\
  &= g''(\int f(u(x))\,\mathrm{d}x) \int f'(u(x)) \delta u(x) \mathrm{d}x\int f'(u(x)) \tau u(x) \mathrm{d}x \\
  &\;\;\;\;+ g'(\int f(u(x))\,\mathrm{d}x) \int f''(u(x)) \delta u(x) \tau u(x) \mathrm{d}x \\
  &= \int \left(g''(\int f(u(x))\,\mathrm{d}x) \int f'(u(x)) \delta u(x) \mathrm{d}x\right)
 f'(u(x)) \tau u(x) \mathrm{d}x \\
 &\;\;\;\;+ \int g'(\int f(u(x))\,\mathrm{d}x)f''(u(x)) \delta u(x) \tau u(x) \mathrm{d}x.
\end{align*}
Consequently, the second derivative can be calculated as one boundary integral, if 
the values of 
\[
\int f(u(x))\,\mathrm{d}x \quad \text{and} \quad \int f'(u(x)) \delta u(x) \mathrm{d}x
\]
in the tangent direction $\delta u$ are available by pre-computations.

To do so in the present example, the following modifications are needed in the cost functional:
\begin{itemize}
\item There is a method \texttt{AlgebraicValue} which calculates $0.5 x^2$ for a given value $x$
- here the pre-computed value of the drag.
\item In the method \texttt{BoundaryValue}, we have to distinguish several cases.
  based upon the problem type evaluated. The current value can be accessed by
  \texttt{GetProblemType()} and if this matches
  \begin{description}
    \item[cost\_functional\_pre] then we must calculate the drag-value, i.e., $k(u)$.
    \item[cost\_functional\_pre\_tangent] then we must calculate the derivative of 
      the drag in direction $\delta u$ (the provided tangent-direction), i.e., $k(\delta u)$ 
      since $k$ is linear in its argument.
    \item[cost\_functional] then we must calculate the rest of the functional. Here only the integral
      over the control costs is needed.
  \end{description}
\item In the methods \texttt{BoundaryValue\_U} and \texttt{BoundaryValue\_UU} we calculate
  the entire derivative w.r.t $u$ (or second derivative respectively) as one integral 
  using the formulas for the first and second derivative, respectively. The needed
  values, i.e.,
  \[
  \int f(u)\mathrm{d}x = \int_{\Gamma_O} n \cdot \sigma(v,p)\,d \mathrm{d}s 
  \]
  and 
  \[
  \int f'(u(x)) \delta u(x) \mathrm{d}x = \int_{\Gamma_O} n \cdot \sigma(\delta v,\delta p)\,d \mathrm{d}s 
  \]
  are available as \texttt{ParamValues} with the respective labels 
  \texttt{cost\_functional\_pre} and \texttt{cost\_functional\_pre\_tangent}.

  Notice, that both \texttt{ParamValues} are a vector of the size given 
  by \texttt{unsigned int NeedPrecomputations() const}. I.e. if multiple functional parts 
  need a pre-integration these can be calculated in an arbitrary number of pre-integration runs.
  In the case of multiple pre-integrations the method \texttt{*Value} needs not only to
  consider the value of \texttt{GetProblemType()} but also the respective \texttt{GetProblemNum()}
  running between $0$ and \texttt{NeedPrecomputations()}$-1$. 
  The order in the ParamValues Vector corresponds to the chosen order of integration.
\end{itemize}

### 2018-10-17 Examples/OPT/StatPDE/Example2/content.tex
Update Doku in Einklang mit Christians und Winnis Bemerkungen/Zustimmung
add examples to parallel-dev

\subsubsection{General problem description}
This example solves the following pointwise minimization problem
\begin{align*}
\min_{(q,u)\in \mathbb R^3 \times H_0^1(\Omega; \mathbb R^2)} J(q,u) &= \frac{1}{2} \sum_{i=0}^2\abs{(u-\overline u)(x_i)}^2 + \frac{\alpha}{2}\|q\|^2&&\\
\text{s.t. } (\nabla u,\nabla \phi) &= (f(q),\phi) \quad\forall\,\phi \in H^1_0(\Omega; \mathbb R^2)
\end{align*}
on the domain $\Omega = [0,1]^2$, with zero Dirichlet boundary conditions and
\begin{itemize}
\item the observation points
\begin{align*}
x_0 = (0.5, 0.5), \quad x_1 = (0.5, 0.25),\quad x_2 = (0.25, 0.25),
\end{align*}
\item the regularization parameter $\alpha = 0$, 
\item the right hand side
\begin{align*}
 f(q) &= q_0 \left(\begin{matrix}2\pi^2  \sin( \pi x) \sin(\pi y)\\0 \end{matrix}\right)\\
      &+ q_1 \left(\begin{matrix}5\pi^2  \sin( \pi x) \sin(2\pi y)\\0 \end{matrix}\right)\\
      &+ q_2 \left(\begin{matrix}0 \\8\pi^2  \sin(2\pi x) \sin(2\pi y)\end{matrix}\right)\\
\end{align*}
\item and the exact solution given by 
\begin{align*}
 \overline{q} &= \bigl(1;0.5;1\bigr)\\
 \overline{u}& = \left(\begin{matrix} \sin( \pi x)( \sin(\pi y)+0.5\sin(2\pi y))\\\sin(2\pi x) \sin(2\pi y) \end{matrix}\right).
\end{align*}
\end{itemize}
\subsubsection{Program description}
{
In contrast to the first example, the control is now a discrete quantity (for
the three observation points) where we use the \texttt{FE\underline{}Nothing}
element to assign the three controls. Here, the number of components equals
the number of controls. 
In addition, }notice that the cost functional is of mixed type (from our computational point of view), i.e. the first part is a pointfunctional whereas the regularization part requires the evaluation of a domain integral. To handle this, we need a special integrator as well as a special newtonsolver. Additionally, our \texttt{LocalFunctional} returns as his type:
\begin{verbatim}
      string
      GetType() const
      {
        return "point domain";
      }
\end{verbatim}
This brings along that we have not only to implement {\color{red}the methods
\begin{align*} 
 &\texttt{ElementValue},&&
 \texttt{ElementValue\_U},\\
 &\texttt{ElementValue\_Q}, &&
 \texttt{ElementValue\_UU},\\
 &\texttt{ElementValue\_UQ},&&
 \texttt{ElementValue\_QU},\\
 &\texttt{ElementValue\_QQ},
\end{align*}}
 from \texttt{FunctionalInterface}, but also all the aforementioned methods with a preceding \text{Point} (\texttt{PointValue} etc.).
%FE_Nothing, handle of the control erlaeutern.

>>>>

\subsubsection{General problem description}
This example solves the following pointwise minimization problem
\begin{align*}
\min_{(q,u)\in \mathbb R^3 \times H_0^1(\Omega; \mathbb R^2)} J(q,u) &= \frac{1}{2} \sum_{i=0}^2\abs{(u-\overline u)(x_i)}^2 + \frac{\alpha}{2}\|q\|^2&&\\
\text{s.t. } (\nabla u,\nabla \phi) &= (f(q),\phi) \quad\forall\,\phi \in H^1_0(\Omega; \mathbb R^2)
\end{align*}
on the domain $\Omega = [0,1]^2$, with zero Dirichlet boundary conditions and
\begin{itemize}
\item the observation points
\begin{align*}
x_0 = (0.5, 0.5), \quad x_1 = (0.5, 0.25),\quad x_2 = (0.25, 0.25),
\end{align*}
\item the regularization parameter $\alpha = 0$, 
\item the right hand side
\begin{align*}
 f(q) &= q_0 \left(\begin{matrix}2\pi^2  \sin( \pi x) \sin(\pi y)\\0 \end{matrix}\right)\\
      &+ q_1 \left(\begin{matrix}5\pi^2  \sin( \pi x) \sin(2\pi y)\\0 \end{matrix}\right)\\
      &+ q_2 \left(\begin{matrix}0 \\8\pi^2  \sin(2\pi x) \sin(2\pi y)\end{matrix}\right)\\
\end{align*}
\item and the exact solution given by 
\begin{align*}
 \overline{q} &= \bigl(1;0.5;1\bigr)\\
 \overline{u}& = \left(\begin{matrix} \sin( \pi x)( \sin(\pi y)+0.5\sin(2\pi y))\\\sin(2\pi x) \sin(2\pi y) \end{matrix}\right).
\end{align*}
\end{itemize}
\subsubsection{Program description}
{
In contrast to the first example, the control is now a discrete quantity (for
the three observation points) where we use the \texttt{FE\underline{}Nothing}
element to assign the three controls. Here, the number of components equals
the number of controls. 
In addition, }notice that the cost functional is of mixed type (from our computational point of view), i.e. the first part is a pointfunctional whereas the regularization part requires the evaluation of a domain integral. To handle this, we need a special integrator as well as a special newtonsolver. Additionally, our \texttt{LocalFunctional} returns as his type:
\begin{verbatim}
      string
      GetType() const
      {
        return "point domain";
      }
\end{verbatim}
Indicating, we have both some point values in the functional, as well as a domain contribution, 
i.e., we calculate $\|q\| = \int_\Omega |q|\,dx$,
even though this in not necessary, since $\alpha =0$ and the euclidean 
norm of $q\in \mathbb R^3$ could be evaluated more easily using an \text{AlgebraicValue} in the functional.

This brings along that we have not only to implement {the methods
\begin{align*} 
 &\texttt{ElementValue},&&
 \texttt{ElementValue\_U},\\
 &\texttt{ElementValue\_Q}, &&
 \texttt{ElementValue\_UU},\\
 &\texttt{ElementValue\_UQ},&&
 \texttt{ElementValue\_QU},\\
 &\texttt{ElementValue\_QQ},
\end{align*}}
 from \texttt{FunctionalInterface}, but also all the aforementioned methods with a preceding \text{Point} (\texttt{PointValue} etc.).
%FE_Nothing, handle of the control erlaeutern.

### 2018-10-17 Examples/OPT/StatPDE/Example7/content.tex
add examples to parallel-dev

We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $0.5$. Its implementation is 
provided in \texttt{localconstraints.h} where the global constraint is handled as 
a functional, which again is normalized to be nonpositive if the control is feasible.

>>>>

We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $V_{\max} = 0.5$, i.e.,
\[
 \int_\Omega q - V_{\max} \,dx \le 0.
\]
Its implementation is 
provided in \texttt{localconstraints.h} where the global constraint is handled as 
a functional, which again is normalized to be nonpositive if the control is feasible.

### 2018-10-17 Examples/PDE/InstatPDE/Example6/content.tex
add examples to parallel-dev

We begin by describing the setting for a pure poroelastic setting, 
the so-called pay-zone.
Let $\Omega_B$ the domain of interest and $\partial\Omega_B$ its boundary
with the partition:
\begin{equation*}
\partial\Omega_B = \Gamma_u \cup \Gamma_t = \Gamma_p \cup \Gamma_f,
\end{equation*}
where $\Gamma_u$ denotes the displacement boundary (Dirichlet), $\Gamma_t$ the 
total stress or traction boundary (Neumann), $\Gamma_p$ the pore 
pressure boundary (Dirichlet), and $\Gamma_f$ the fluid flux boundary
(Neumann). Concretely, we have for a material 
with the displacement variable $u$ and its 
Cauchy stress tensor $\sigma$:
\begin{align*}
u &= \bar{u} \quad \text{on } \Gamma_u, \\
\sigma n &= \bar{t} \quad \text{on } \Gamma_t, 
\end{align*}
for given $\bar{u}$ and $\bar{t}$, and the 
normal vector $n$. 
For the pressure with the permeability tensor 
$K$ and fluid's viscosity $\eta_f$, we have the conditions:
\begin{align*}
p &= \bar{p} \quad \text{on } \Gamma_p, \\
- \frac{K}{\eta_f} \Bigl( \nabla p - \rho_f g\Bigr) \cdot n &= \bar{q}\quad \text{on } \Gamma_f,
\end{align*}
for given $\bar{p}$ and $\bar{q}$; and the density $\rho_f$ and the gravity $g$.
For the initial conditions at time $\tau=0$, we prescribe
\begin{align*}
p(\tau =0) = p_0 \quad \text{in } \Omega_B,\\
\sigma(\tau =0) = \sigma_0 \quad \text{in } \Omega_B,
\end{align*}
In this case of this extension
(if $\Omega_B$ is totally embedded in $\Omega_S$)
the boundary conditions on $\partial\Omega_B$ reduce 
to interface conditions $\partial\Omega_B :=\Gamma_i =
\Omega_B \cap \Omega_S$.
Let $I:=[0,T]$ denote the time interval.
The underlying Biot system reads:
Find the pressure $p_{\text{B}}$ and displacement 
$u_{\text{B}}$ such that
\begin{align*}
\partial_t (c_B p_{\text{B}} + \alpha_B \text{div}u_{\text{B}})\\ -
\frac{1}{\eta_f} \text{div}\, K 
(\nabla p_{\text{B}} - \rho_f g) &= q \quad \text{in }\Omega_{B} \times I, \\
- \text{div}\bigl( \sigma_B (u) \bigr)
+ \alpha_B\nabla p_{\text{B}} &= f_{\text{B}} 
\quad \text{in }\Omega_{\text{B}} \times I,
\end{align*}
with
\[
\sigma_B(u_B) := \mu_B(\nabla u_{\text{B}} + \nabla u_{\text{B}}^T) +  
\lambda_B\text{div}\, u_{\text{B}}I,
\]
and the coefficients $c_B\geq 0$, 
the Biot-Willis constant $\alpha_B \in [0,1]$,
(in fact, this constant relates to the amount of 
coupling between the flow part and the elastic part) 
and the permeability tensor $K$, 
fluid's viscosity and its density 
$\eta_f$ and $\rho_f$, gravity $g$ and a volume 
source term $q$ (i.e., usually, wells for oil production and
fluid injection). In the second equation,
the Lam\'e coefficients are denoted 
by $\lambda_B >0$ and $\mu_B >0$ 
and $f_{\text{B}}$ is a volume force.

The velocity $v_{\text{B}}$ 
in the porous medium is obtained 
with the help of Darcy's law (Darcy 1856)
and the Darcy equations which are obtained 
through homogenization of Stokes's equations
It holds:
\begin{equation*}
v_{\text{B}} = -\frac{1}{\eta_f} K(\nabla p_{\text{B}} - \rho_f g).
\end{equation*}
Usually the non-pay zone is described 
in terms of linear elasticity: Find 
a displacement $u_S$ such that
\begin{align*}
- \text{div}\bigl( \sigma_S (u_S)  \bigr) = f_S \quad \text{in }\Omega_{\text{S}} \times I,
\end{align*}
with
\begin{align*}
\sigma_S (u_S) := \mu_S(\nabla u_{\text{S}} + \nabla u_{\text{S}}^T) +  
\lambda_S\text{div}\, u_{\text{S}}I, 
\end{align*}
with the Lam\'e coefficients $\mu_S$ and $\lambda_S$
and a volume force $f_S$. On the boundary 
$\partial\Omega_S := \Gamma_D \cup \Gamma_N$, the 
conditions
\begin{equation*}
u_S = \bar{u}_S \quad\text{on } \Gamma_D , \quad \sigma_S (u_S) n_S = \bar{t}_S \quad\text{on } \Gamma_N,
\end{equation*}
are prescribed with given $\bar{u}_S$ and $\bar{t}_S$.

It finally remains to describe the interface 
conditions on $\Gamma_{i}$ between the two sub-systems:
\begin{equation}
\label{interface_conditions}
\begin{aligned}
u_{\text{B}} &= u_S ,   \\
\sigma_{B}(u_B)n_B - \sigma_S(u_S)n_S &= 
\alpha p_{\text{B}} n_B  , \\
-\frac{1}{\eta_f} K(\nabla p_{\text{B}} - \rho_f g) \cdot n_S &= 0. 
\end{aligned} 
\end{equation}
It is important to notice that the second condition 
in \eqref{interface_conditions}, requires careful 
implementation on the interface, which is 
carried out with the help of deal.II's FE Nothing element.

>>>>

We begin by describing the setting for a pure poroelastic setting, 
the so-called pay-zone.
Let $\Omega_B$ the domain of interest and $\partial\Omega_B$ its boundary
with the partition:
\begin{equation*}
\partial\Omega_B = \Gamma_u \cup \Gamma_t = \Gamma_p \cup \Gamma_f,
\end{equation*}
where $\Gamma_u$ denotes the displacement boundary (Dirichlet), $\Gamma_t$ the 
total stress or traction boundary (Neumann), $\Gamma_p$ the pore 
pressure boundary (Dirichlet), and $\Gamma_f$ the fluid flux boundary
(Neumann). Concretely, we have for a material 
with the displacement variable $u$ and its 
Cauchy stress tensor $\sigma$:
\begin{align*}
u &= \bar{u} \quad \text{on } \Gamma_u, \\
\sigma n &= \bar{t} \quad \text{on } \Gamma_t, 
\end{align*}
for given $\bar{u}$ and $\bar{t}$, and the 
normal vector $n$. 
For the pressure with the permeability tensor 
$K$ and fluid's viscosity $\eta_f$, we have the conditions:
\begin{align*}
p &= \bar{p} \quad \text{on } \Gamma_p, \\
- \frac{K}{\eta_f} \Bigl( \nabla p - \rho_f g\Bigr) \cdot n &= \bar{q}\quad \text{on } \Gamma_f,
\end{align*}
for given $\bar{p}$ and $\bar{q}$; and the density $\rho_f$ and the gravity $g$.
For the initial conditions at time $\tau=0$, we prescribe
\begin{align*}
p(\tau =0) = p_0 \quad \text{in } \Omega_B,\\
\sigma(\tau =0) = \sigma_0 \quad \text{in } \Omega_B,
\end{align*}
In this case of this extension
(if $\Omega_B$ is totally embedded in $\Omega_S$)
the boundary conditions on $\partial\Omega_B$ reduce 
to interface conditions $\partial\Omega_B :=\Gamma_i =
\Omega_B \cap \Omega_S$.
Let $I:=[0,T]$ denote the time interval.

\begin{Problem}[The Biot system]
Find the pressure $p_{\text{B}}$ and displacement 
$u_{\text{B}}$ such that
\begin{align*}
\partial_t (c_B p_{\text{B}} + \alpha_B \text{div}u_{\text{B}})\\ -
\frac{1}{\eta_f} \text{div}\, K 
(\nabla p_{\text{B}} - \rho_f g) &= q \quad \text{in }\Omega_{B} \times I, \\
- \text{div}\bigl( \sigma_B (u) \bigr)
+ \alpha_B\nabla p_{\text{B}} &= f_{\text{B}} 
\quad \text{in }\Omega_{\text{B}} \times I,
\end{align*}
with
\[
\sigma_B(u_B) := \mu_B(\nabla u_{\text{B}} + \nabla u_{\text{B}}^T) +  
\lambda_B\text{div}\, u_{\text{B}}I,
\]
and the coefficients $c_B\geq 0$, 
the Biot-Willis constant $\alpha_B \in [0,1]$,
(in fact, this constant relates to the amount of 
coupling between the flow part and the elastic part) 
and the permeability tensor $K$, 
fluid's viscosity and its density 
$\eta_f$ and $\rho_f$, gravity $g$ and a volume 
source term $q$ (i.e., usually, wells for oil production and
fluid injection). In the second equation,
the Lam\'e coefficients are denoted 
by $\lambda_B >0$ and $\mu_B >0$ 
and $f_{\text{B}}$ is a volume force.
\end{Problem}

The velocity $v_{\text{B}}$ 
in the porous medium is obtained 
with the help of Darcy's law (Darcy 1856)
and the Darcy equations which are obtained 
through homogenization of Stokes's equations
It holds:
\begin{equation*}
v_{\text{B}} = -\frac{1}{\eta_f} K(\nabla p_{\text{B}} - \rho_f g).
\end{equation*}

Usually the non-pay zone is described 
in terms of linear elasticity: 
\begin{Problem}
Find 
a displacement $u_S$ such that
\begin{align*}
- \text{div}\bigl( \sigma_S (u_S)  \bigr) = f_S \quad \text{in }\Omega_{\text{S}} \times I,
\end{align*}
with
\begin{align*}
\sigma_S (u_S) := \mu_S(\nabla u_{\text{S}} + \nabla u_{\text{S}}^T) +  
\lambda_S\text{div}\, u_{\text{S}}I, 
\end{align*}
with the Lam\'e coefficients $\mu_S$ and $\lambda_S$
and a volume force $f_S$. On the boundary 
$\partial\Omega_S := \Gamma_D \cup \Gamma_N$, the 
conditions
\begin{equation*}
u_S = \bar{u}_S \quad\text{on } \Gamma_D , \quad \sigma_S (u_S) n_S = \bar{t}_S \quad\text{on } \Gamma_N,
\end{equation*}
are prescribed with given $\bar{u}_S$ and $\bar{t}_S$.
\end{Problem}

It finally remains to describe the interface 
conditions on $\Gamma_{i}$ between the two sub-systems:
\begin{equation}
\label{interface_conditions}
\begin{aligned}
u_{\text{B}} &= u_S ,   \\
\sigma_{B}(u_B)n_B - \sigma_S(u_S)n_S &= 
\alpha p_{\text{B}} n_B  , \\
-\frac{1}{\eta_f} K(\nabla p_{\text{B}} - \rho_f g) \cdot n_S &= 0. 
\end{aligned} 
\end{equation}

\subsubsection{Program description}
In this example, the crucial aspect (from mathematical point of view 
as well as from the implementation) are the interface conditions
\eqref{interface_conditions}.
Here, it is important to notice that the second condition 
in \eqref{interface_conditions}, requires careful 
implementation on the interface, which is 
carried out with the help of deal.II's FE Nothing element.
Second, please do not forget to activate the flag
\begin{verbatim}
      HasFaces() const
      {
        return true;
      }
\end{verbatim}

The problem is driven by traction forces (Neumann conditions), which 
are imposed via the 
\begin{verbatim}
      void
      BoundaryEquation(...)
      {
        ...   
      }
\end{verbatim}

As functionals, we evaluate the pressure in two different 
points of the domain. The observation should be that the 
pressure first starts increasing reaching a maximum and then
starts decaying. This is the so-called Mandel-Creyer effect.
